Repeatability Test

### 2017-09-28 mlppi-ksii17/review/review_response.tex

\clearpage
\section*{Reviewer 1}\label{sec:rev1}

% 1
\rev{
[Reviewer(s)' Comments to Author]:
Reviewer: 1

Comments to the Author
Generally Fig1. is not a figure scale and can be considered as a structure rather aha a Fig. 1. technically, the primary figures are the general scale and structure of the method which tends to grasp the authors' attention and must be clarified. 
}

We totally agree with you. The old Fig. 1 is not at a real figure. We feel that it had better be put into a table for further reference, which is now {\color{blue}\underline{Tab. 1}}.

@@

\rev{
The presented Wizard Architecture in Fig. 2 needs to be expanded. 
}

We significantly expanded the architecture, which is now {\color{blue}\underline{Fig. 1}}, with a specified description of each phase. In addition, 
the figure now includes (1) the query workload example on the top and (2) the output solution 
produced by the wizard on the bottom, for better clarification.

\rev{
The table in Page3 does not have any caption to introduces besides, its location is badly organized.
}
Thanks for the comments. To address your concern, we put in tabular form not only that table with no caption but also 
some other provided examples. We then positioned those new tables on the top of each page in the introduction in the revised.

@@

\rev{
The main contribution of the paper is so limited and needs to be extended in Section 1. 
}

We took out some contributions mentioned in Section 2 (now Section 3) and then incorporated them into the contribution paragraph (on page~5 
in the revision), which is now substantially extended.

\rev{ 
In the experiment environmental setting, the deployment in realistic datasets are missing and must be indicated for the reproduction of the future readers.  
}

\rev{
According to the bar-shaped results, the WIZARD does not provide optimal results compared to the state-of the arts. They must clearly be expressed how this cases can be used in the real-time scenarios. 
}

@@

\rev{
Also, Authors should give a more clear definition of the "application type" used in the paper. For example, what information of applications are used and how to obtain this information. 
}

\rev{
Last but not least backs to the background which is limited and some hot-related works are missing that are listed in i)"Using imperialist competition algorithm for independent task scheduling in grid computing" and ii) "A hybrid metaheuristic algorithm for Job scheduling on computational grids" that addressed the analytical workload exploitation in the real case studies that must be added in the background to make your work holistic for the future readers.
}
OK, we now have some mentions of the above two works compared to our work. Also, we added these two in the references in the revision.

@@

\clearpage
\section*{Reviewer 2}\label{sec:rev2}

% 2
\rev{
Reviewing: 2

Comments to the Author
The paper could be published after addressing following comments:
1. Abstract could be better write, in this reviewer point of view, the current abstract is not comprehensive.
}

\rev{
2. The manuscript could be better organize as well. For instance, the related works section could be placed after introduction section no before conclusion.
}
A great suggestion. We have relocated the related work section right after the introduction in the revised manuscript. Note that there are also some  references newly added in that section for completeness.

@@

\rev{
3. Providing a comparison table could be useful for readers.
}

\rev{
4. Conclusion is too long.
}

\rev{
5. Introduction section need more references.
}
We've added some references in the contribution paragraph in the introduction on page 5.

### 2017-09-29 mlppi-ksii17/review/review_response.tex

Comments to the Author
Generally Fig1. is not a figure scale and can be considered as a structure rather aha a Fig. 1. technically, the primary figures are the general scale and structure of the method which tends to grasp the authors' attention and must be clarified. 
}

We totally agree with you. The old Fig. 1 is not at a real figure. We feel that it had better be put into a table for further reference, which is now {\color{blue}\underline{Tab. 1}}.

\rev{
The presented Wizard Architecture in Fig. 2 needs to be expanded. 
}

We significantly expanded the architecture, which is now {\color{blue}\underline{Fig. 1}} on page~7, with a specified description of each phase. In addition, the figure now includes (1) the query workload text exemplified in the paper (on the top) and (2) the output solution 
produced by the wizard (on the bottom), for better clarification.

\rev{
The table in Page3 does not have any caption to introduces besides, its location is badly organized.
}
Thanks for the comments. To address your concern, we put in tabular form the table with its caption on page~2 (now, {\color{blue}Tab.~2}). 
Note that we tabularized other examples for better exposition in the introduction.

\rev{
The main contribution of the paper is so limited and needs to be extended in Section 1. 
} 
We took out some contributions mentioned in Section 2 (now Section 3) and then incorporated them into the contribution paragraph (on page~5 
in the revision), which is now substantially extended.

@@

\rev{ 
In the experiment environmental setting, the deployment in realistic datasets are missing and must be indicated for the reproduction of the future readers.  
}

%Even though our query workloads (similar to {\em q1} in Tab.~3) are synthetic, the queries were generated from a realistic query template, 
%which is from customer cases like reports and form templates. The queries are of type joining a fact table and a dimension table in a popular benchmark, representing a real analytical workload. In addition, the proposed wizard allows for general expressions for partitioning definition as addressed in the solution paragraph in the introduction. Hence, the results on our workloads do not lose their validity on a real environment. Please refer to the third and subsequent paragraphs in Section~5.1 (on page 16).
The synthetic queries used for our experiments were generated from a realistic query template, which is from customer cases like reports and form templates. The queries are of type joining a fact table and a dimension table in a popular benchmark, representing a real analytical workload. 
In addition, the proposed wizard allows for general expressions for partitioning definition as addressed in the solution paragraph in the introduction. Hence, the results on our workloads do not lose their validity on a real environment. For more details, please refer to the Solution paragraph in the introduction and the third and subsequent paragraphs in Section~5.1.

@@

\rev{
According to the bar-shaped results, the WIZARD does not provide optimal results compared to the state-of the arts. They must clearly be expressed how this cases can be used in the real-time scenarios. 
}

Your confusion comes from Figure 5 in the original submission. The proposed wizard obviously outperforms the compared approaches: no partitioning (NO PPI) and a human expert (EXP). For better clarification, we removed that figure and instead provided a comparison table. Again, our query workloads are from the real benchmark, SSB, and our algorithm is still applicable to any other type of analytical workload, since the search space is driven by the query predicates extracted from the workload.

\rev{
Also, Authors should give a more clear definition of the ``application type" used in the paper. For example, what information of applications are used and how to obtain this information. 
}

We understand your concern. The application type of the proposed wizard is a \underline{physical database design tool} (fundamentally different from several existing works [4--6]. Also note that any complex workload, giving many different partitioning options, can benefit from the automated wizard to find almost an optimal solution. For more details, please refer to the first, third, and fourth bullets in the Contribution paragraphs in the Introduction.

\rev{
Last but not least backs to the background which is limited and some hot-related works are missing that are listed in i)"Using imperialist competition algorithm for independent task scheduling in grid computing" and ii) "A hybrid metaheuristic algorithm for Job scheduling on computational grids" that addressed the analytical workload exploitation in the real case studies that must be added in the background to make your work holistic for the future readers.
}

OK, we now have some mentions of the above two works compared to our work. Also, we added these two in the references in the revision.

@@

Comments to the Author
The paper could be published after addressing following comments:
1. Abstract could be better write, in this reviewer point of view, the current abstract is not comprehensive.
}

\rev{
2. The manuscript could be better organize as well. For instance, the related works section could be placed after introduction section no before conclusion.
}
A great suggestion. We have relocated the related work section right after the introduction in the revised manuscript. Note that there are also some  references newly added in that section for completeness.

\rev{
3. Providing a comparison table could be useful for readers.
}

Yes, we do now provide Tab. 9 for better clarity on the comparison.

### 2017-09-30 pt_characterization/rep_check/res1.tex
PT characterizing

\paragraph{Stacked Histograms in a 3D Plot:}
Figure~\ref{fig:hist3d} represents a 3D plot of collecting the histograms of PT 
exhibited in Section~\ref{sec:1st_pt}. 
Note that the histograms from the task lengths of 8192 and 16384 seconds 
to be shown in Figures~\ref{fig:inc8192_r2_hist_v5} and~\ref{fig:inc16384_r2_hist_v5}. 
are brought into Figure~\ref{fig:hist3d} for completeness. The x-, y-, z-axes 
indicate the normalized PT ranging from 0 to 100, task length in log scale, 
and relative frequency of each histogram, such that for each INC 
it is scaled from 0 (the shortest) to 100 (the highest).

\begin{figure}[htp!]
%\vspace{-.3in}
	\centering
	%\includegraphics[scale=0.6,angle=270]{u_s_time/3d_plot.eps}\label{fig:3d_plot}
	%\includegraphics[scale=0.6]{u_s_time/new_3d_plot}\label{fig:3d_plot}
	\includegraphics[scale=1]{u_s_time/new_3d_plot}\label{fig:3d_plot}
	\caption{3D histograms on INC~\label{fig:hist3d}}
\end{figure}

@@

\paragraph{Fitting Histograms in Bi-Normal Distributions:}
We ran Rob's code to obtain a bi-normal fit for each INC's run. 
Table~\ref{tab:binormal_fit} exhibits the two means (modes), standard deviations, and scales for each of the INC runs.

>>>>

\paragraph{Stacked Histograms in a 3D Plot:}
Figure~\ref{fig:hist3d} represents a 3D plot of collecting the histograms of PT in Section~\ref{sec:1st_pt}. 
Note that we additionally include the histograms from the task lengths of 8192 and 16384 seconds, which will be shown in Figures~\ref{fig:inc8192_r2_hist_v5} and~\ref{fig:inc16384_r2_hist_v5} (on page~47). See the legend in the right hand side of the figure, for more details about specific task length information.
%To obtain the better shape, we remove from those histograms outliers identified via the second step of EMPv5.
The x-axis corresponds to the normalized PT relative to the minimum, ranging 0 to 100, the y-axis to task length in log scale, and the z-axis to the normalized frequency relative to the highest bar for each histogram.

There are several interesting things to notice. First, INC32 has some empty bins in the raw histogram in Figure ~\ref{fig:inc32_r1_et_hist_v5}, thereby zero value on the x-axis for that histogram in brown in Figure~\ref{fig:hist3d}.

\begin{figure}[htp!]
%\vspace{-.3in}
	\centering
	%\includegraphics[scale=0.6,angle=270]{u_s_time/3d_plot.eps}\label{fig:3d_plot}
	%\includegraphics[scale=0.6]{u_s_time/new_3d_plot}\label{fig:3d_plot}
	\includegraphics[scale=1]{u_s_time/new_3d_plot}\label{fig:3d_plot}
	\caption{3D histograms of PT on doubly-increasing INC~\label{fig:hist3d}}
\end{figure}

@@

\paragraph{Fitting PT Histograms in Bi-Normal Distributions:}
We ran Rob's code to obtain a bi-normal fit for each INC's PT histogram 
in Section~\ref{sec:first_run}. 
Table~\ref{tab:binormal_fit} exhibits the two means (modes), standard deviations, and scales for the PT histogram associated with each INC.
